paper

### 2020-02-20 analysis/paper.Rmd
edit paper

---
title: "paper"
author: "A group of fabulous contributors"
date: "2/19/2020"
output: html_document
---

@@

## Overview
This is a R Markdown file which can be knit to produce the target figures as the goal of our replication. This __analysis__ folder also have R script files that are used by the R Markdown file.  It should not have any files that are not used by the R Markdown file.

## Goal

## Specification

## Summary

## Open Questions

>>>>

---
Title: "A replication of a simulation study on measuring and correcting bias of under-5 mortality estimation in populations affected by HIV/AIDS"
Author:
  - name: Name Surname
    affiliation: 1
  - name: Name Surname,
    affiliation: 2, 3
Address:
  - code:    1
    address: Affiliation Dept/Program/Center, Institution Name, City, State, Country
  - code:    2
    address: Affiliation Dept/Program/Center, Institution Name, City, State, Country
  - code:    3
    address: Affiliation Dept/Program/Center, Institution Name, City, State, Country
Contact:
  - corresponding-author@mail.com
Editor:
  - Name Surname
Reviewer:
  - Name Surname
  - Name Surname
Publication:
  received:  Sep, 1, 2015
  accepted:  Sep, 1, 2015
  published: Sep, 1, 2015
  volume:    "**1**"
  issue:     "**1**"
  date:      Sep 2015
  number: 1
Repository:
  article:   
  code:      
  data:      
  notebook:  
Reproduction:
  - "Original article (title, authors, journal, doi)"
bibliography:
  bibliography.bib
output:
  output: word_document
---

# Introduction
This is a R Markdown file which can be knit to produce the target figures as the goal of our replication. This __analysis__ folder also have R script files that are used by the R Markdown file.  It should not have any files that are not used by the R Markdown file.

@@

```{r}
x <- 1 + 1
```

## ...

## ...

## Result

## Conclusion

## References cited
